\normalsize \headingfont \textbf{Holier Than Thou? No Large Partisan Gaps in the Consumption of Pornography Online} \vspace{-1.5em}

### 2024-04-28 ms/main.tex
Updates from Overleaf

\subsection{Demographics And Partisan Identification}
\label{subsec:demographics}
YouGov panel file contains data on demographic characteristics like birth year, state of residence, gender, race, and education level. It also contains data on partisan self-identification. Except for 120 respondents who did not respond or picked ``not sure'' or ``don't know,'' the rest selected the party they identified with or marked themselves as independents. Of the 1,080 people, 82\% leaned either Republican or Democrat. The remaining 18 percent identified as independent. (See Panel B of \cref{tab:characteristics_split_by_party} and \cref{tab:characteristics_split_by_porn_consumers} for a summary of socio-demographic data by party.)

@@

Partisans differ on other characteristics than the party (see \cref{tab:characteristics_split_by_party}). For instance, Democrats are younger (\cref{tab:characteristics_split_by_party}). Add to it that consumers of pornography online tend to be younger (see Panel B of \cref{tab:characteristics_split_by_porn_consumers}). How do differences in age and other such demographic differences between the parties ``explain'' the results? To find out, we control for the following immutable characteristics that predict pornography consumption: age \citep{Wright2013-an, Woodrum1992-vk}, ethnicity \citep{Wright2013-an}, gender \citep{Woodrum1992-vk}, and education level \citep{Woodrum1992-vk}. As \cref{fig:quantile_regression_duration_covariates} and \cref{fig:quantile_regression_prop_duration_covariates} show, once we adjust for confounders, the partisan differences melt away. 
%(For the corresponding table with the various percentiles, see \cref{tab:quantile-estimates-time}.) 
%Using alternative classifications of pornography sites led to similar conclusions (\cref{sec:robustness}).

@@

%==============================================================================
% Table for balance of porn consumption and individual characteristics by party
% Difference in medians
%==============================================================================
\begin{table}[ht] \centering \small \setlength\tabcolsep{5 pt}
	\caption{Differences (in Medians) in Pornography Consumption}
	\label{tab:characteristics_split_by_party_medians}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{@{\hspace{0\tabcolsep}}llrcccrr@{\hspace{0\tabcolsep}}}
			\toprule
			&\multicolumn{7}{c}{\underline{Measures of pornography consumption}}\\
			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Democrats}&\multicolumn{1}{c}{Republicans}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
			\cmidrule{2-8}
			\input{../tabs/balance_outcomes_by_party_medians.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\scriptsize \emph{Notes:}
		The table shows splits by party for pornography consumption and for individual characteristics for the 1,200 individuals.
		This table focuses on differences in medians.
		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
		Column (1) shows subgroups for categorical variables.
		Column (2) indicates the count of missing variables, if any.
		Columns (3)--(5) show the medians, the first quartiles, and the third quartiles for the full sample, Democrats, and Republicans.
		1st and 3rd quartiles in brackets.
		Column (6) and column (7) report the p-values and standardized median differences for Democrats vs Republicans.
		See Panel A of \cref{tab:characteristics_split_by_party} for differences in means.
	}
\end{table}

\begin{table}[ht] \centering \small \setlength\tabcolsep{5 pt}
	\caption{Median Differences in Pornography Consumption}
	\label{tab:characteristics_split_by_party_medians}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{@{\hspace{0\tabcolsep}}lrcccrr@{\hspace{0\tabcolsep}}}
			\toprule
			&\multicolumn{6}{c}{\underline{Measures of pornography consumption}}\\
			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}\\			
			&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Democrats}&\multicolumn{1}{c}{Republicans}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
			\cmidrule{2-7}
        			n                            &            & 1200          & 530           & 356            &                  \\
         Minutes, median [Q1,Q3]      &  65        & 0.0 [0.0,4.8] & 0.0 [0.0,3.1] & 0.0 [0.0,3.6] & 0.981     & 0.056           \\
         \% of time, median [Q1,Q3]    &  65        & 0.0 [0.0,0.1] & 0.0 [0.0,0.1] & 0.0 [0.0,0.1] & 0.842     & 0.049           \\
         Visits, median [Q1,Q3]       &  65        & 0.0 [0.0,8.0] & 0.0 [0.0,6.0] & 0.0 [0.0,8.0] & 0.933     & 0.048           \\
         \% of visits, median [Q1,Q3]  &  65        & 0.0 [0.0,0.2] & 0.0 [0.0,0.1] & 0.0 [0.0,0.2] & 0.916     & 0.085         \\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\scriptsize \emph{Notes:}
		The table shows splits by party for pornography consumption and for individual characteristics for the 1,200 individuals.
		This table focuses on differences in medians.
		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
		Column (1) indicates the count of missing variables.
		Columns (2)--(4) show the medians, the first quartiles, and the third quartiles for the full sample, Democrats, and Republicans, respectively.
		1st and 3rd quartiles in brackets.
		Column (5) and column (6) report the p-values and standardized median differences for Democrats vs Republicans.
		See Panel A of \cref{tab:characteristics_split_by_party} for differences in means.
	}
\end{table}

@@

%==============================================================================
% Table for balance of porn consumption and individual characteristics by party
%==============================================================================
\begin{table}[!ht] \centering \ssmall \setlength\tabcolsep{9 pt}
	\caption{Differences in Pornography Consumption and Individual Characteristics by Party}
	\label{tab:characteristics_split_by_party}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{@{\hspace{0\tabcolsep}}llrcccrr@{\hspace{0\tabcolsep}}}
			\toprule
			&\multicolumn{7}{c}{\underline{Panel A. Measures of pornography consumption}}\\
			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Democrat}&\multicolumn{1}{c}{Republican}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
			\cmidrule{2-8}
			\input{../tabs/balance_outcomes_by_party.tex}\\
			%-------------------------------------------------------------------
			\cmidrule{2-8}
			&\multicolumn{7}{c}{\underline{Panel B. Individual characteristics}}\\
			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Democrat}&\multicolumn{1}{c}{Republican}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
			\cmidrule{2-8}
			\input{../tabs/balance_covariates_by_party.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\scriptsize \emph{Notes:}
		The table shows splits by party for pornographic consumption and for individual characteristics for the 1,200 individuals.
		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
		Column (1) shows subgroups for categorical variables.
		Column (2) indicates the count of missing variables, if any.
		Columns (3)--(5) show means and standard deviations for continuous variables and count and percentage of data for categorical variables for the full sample, Democratic individuals, and Republican individuals.
		Standard deviations and percentages are in parentheses.
		Column (6) and column (7) report the p-values and standardized mean differences for Democrats vs Republicans.
		Given the skew in consumption of pornography, we also performed tests for differences in medians for the measures of pornography consumption by party (see \cref{tab:characteristics_split_by_party_medians}).
	}
\end{table}

%==============================================================================
% Table for balance of porn consumption and individual characteristics by consumer
%==============================================================================
\begin{table}[ht] \centering \scriptsize \setlength\tabcolsep{6 pt}
	\caption{Differences in Pornography Consumption and Individual Characteristics by Pornography Consumers}
	\label{tab:characteristics_split_by_porn_consumers}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{@{\hspace{0\tabcolsep}}llrcccrr@{\hspace{0\tabcolsep}}}
			\toprule
			&\multicolumn{7}{c}{\underline{Panel A. Measures of pornography consumption}}\\
			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Non-Consumers}&\multicolumn{1}{c}{Consumers}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
			\cmidrule{2-8}
			\input{../tabs/balance_outcomes_by_porn_consumers.tex}\\
			%-------------------------------------------------------------------
			\cmidrule{2-8}
			&\multicolumn{7}{c}{\underline{Panel B. Individual characteristics}}\\
			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Non-Consumers}&\multicolumn{1}{c}{Consumers}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
			\cmidrule{2-8}
			\input{../tabs/balance_covariates_by_porn_consumers.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\scriptsize \emph{Notes:}
		The table shows splits by consumers of pornography for pornography consumption and for individual characteristics for the 1,200 individuals.
		65 of the 1,200 individuals did not clock any browsing activity and are in the first panel.
		These 65 individuals are not substantially different in characteristics than those included in the sample (untabulated).
		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
		Column (1) shows subgroups for categorical variables.
		Column (2) indicates the count of missing variables, if any.
		Columns (3)--(5) show means and standard deviations for continuous variables and count and percentage of data for categorical variables, for the full sample, non-consumers of pornography, and consumers of pornography.
		Standard deviations and percentages are in parentheses.
		Column (6) and column (7) report the p-values and standardized mean differences for non-consumers vs consumers.
	}
\end{table}

>>>>

\subsection{Demographics And Partisan Identification}
\label{subsec:demographics}
YouGov panel file contains data on demographic characteristics like birth year, state of residence, gender, race, and education level. It also contains data on partisan self-identification. Except for 120 respondents who did not respond or picked ``not sure'' or ``don't know,'' the rest selected the party they identified with or marked themselves as independents. Of the 1,080 people, 82\% leaned either Republican or Democrat. The remaining 18 percent identified as independent. (See Panel B of \cref{tab:characteristics_split_by_party} for a summary of socio-demographic data by party.)

@@

Partisans differ on other characteristics than the party (see \cref{tab:characteristics_split_by_party}). For instance, Democrats are younger (\cref{tab:characteristics_split_by_party}). 
%Add to it that consumers of pornography online tend to be younger (see Panel B of \cref{tab:characteristics_split_by_porn_consumers}). 
How do differences in age and other such demographic differences between the parties ``explain'' the results? To find out, we control for the following immutable characteristics that predict pornography consumption: age \citep{Wright2013-an, Woodrum1992-vk}, ethnicity \citep{Wright2013-an}, gender \citep{Woodrum1992-vk}, and education level \citep{Woodrum1992-vk}. As \cref{fig:quantile_regression_duration_covariates} and \cref{fig:quantile_regression_prop_duration_covariates} show, once we adjust for confounders, the partisan differences melt away. 
%(For the corresponding table with the various percentiles, see \cref{tab:quantile-estimates-time}.) 
%Using alternative classifications of pornography sites led to similar conclusions (\cref{sec:robustness}).

@@

%==============================================================================
% Table for balance of porn consumption and individual characteristics by party
% Difference in medians
%==============================================================================
\begin{table}[ht] \centering \normalsize \setlength\tabcolsep{5 pt}
	\caption{Differences (in Medians) in Pornography Consumption}
	\label{tab:characteristics_split_by_party_medians}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{@{\hspace{0\tabcolsep}}llrcccrr@{\hspace{0\tabcolsep}}}
			\toprule
			&\multicolumn{6}{c}{\underline{Measures of pornography consumption}}\\
			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}\\			
			&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Democrats}&\multicolumn{1}{c}{Republicans}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
			\cmidrule{2-7}
			\input{../tabs/balance_outcomes_by_party_medians.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\footnotesize \emph{Notes:}
		The table shows splits by party for pornography consumption and for individual characteristics for the 1,200 individuals.
		This table focuses on differences in medians.
		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
		Column (1) shows subgroups for categorical variables.
		Column (2) indicates the count of missing variables, if any.
		Columns (3)--(5) show the medians, the first quartiles, and the third quartiles for the full sample, Democrats, and Republicans.
		1st and 3rd quartiles in brackets.
		Column (6) and column (7) report the p-values and standardized median differences for Democrats vs Republicans.
		See Panel A of \cref{tab:characteristics_split_by_party} for differences in means.
	}
\end{table}

@@

%==============================================================================
% Table for balance of porn consumption and individual characteristics by party
%==============================================================================
\begin{table}[!ht] \centering \ssmall \setlength\tabcolsep{9 pt}
	\caption{Differences in Pornography Consumption and Individual Characteristics by Party}
	\label{tab:characteristics_split_by_party}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{@{\hspace{0\tabcolsep}}llrcccrr@{\hspace{0\tabcolsep}}}
			\toprule
			&\multicolumn{7}{c}{\underline{Panel A. Measures of pornography consumption}}\\
			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Democrat}&\multicolumn{1}{c}{Republican}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
			\cmidrule{2-8}
			\input{../tabs/balance_outcomes_by_party.tex}\\
			%-------------------------------------------------------------------
			\cmidrule{2-8}
			&\multicolumn{7}{c}{\underline{Panel B. Individual characteristics}}\\
			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Democrat}&\multicolumn{1}{c}{Republican}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
			\cmidrule{2-8}
			\input{../tabs/balance_covariates_by_party.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\scriptsize \emph{Notes:}
		The table shows splits by party for pornography consumption and for individual characteristics for the 1,200 individuals.
		This table focuses on differences in medians.
		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
		Column (1) indicates the count of missing variables.
		Columns (2)--(4) show the medians, the first quartiles, and the third quartiles for the full sample, Democrats, and Republicans, respectively.
		1st and 3rd quartiles in brackets.
		Column (5) and column (6) report the p-values and standardized median differences for Democrats vs Republicans.
		See Panel A of \cref{tab:characteristics_split_by_party} for differences in means.
	}
\end{table}

\iffalse
%==============================================================================
% Table for balance of porn consumption and individual characteristics by consumer
%==============================================================================
\begin{table}[ht] \centering \scriptsize \setlength\tabcolsep{6 pt}
	\caption{Differences in Pornography Consumption and Individual Characteristics by Pornography Consumers}
	\label{tab:characteristics_split_by_porn_consumers}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{@{\hspace{0\tabcolsep}}llrcccrr@{\hspace{0\tabcolsep}}}
			\toprule
			&\multicolumn{7}{c}{\underline{Panel A. Measures of pornography consumption}}\\
			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Non-Consumers}&\multicolumn{1}{c}{Consumers}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
			\cmidrule{2-8}
			\input{../tabs/balance_outcomes_by_porn_consumers.tex}\\
			%-------------------------------------------------------------------
			\cmidrule{2-8}
			&\multicolumn{7}{c}{\underline{Panel B. Individual characteristics}}\\
			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Non-Consumers}&\multicolumn{1}{c}{Consumers}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
			\cmidrule{2-8}
			\input{../tabs/balance_covariates_by_porn_consumers.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\scriptsize \emph{Notes:}
		The table shows splits by consumers of pornography for pornography consumption and for individual characteristics for the 1,200 individuals.
		65 of the 1,200 individuals did not clock any browsing activity and are in the first panel.
		These 65 individuals are not substantially different in characteristics than those included in the sample (untabulated).
		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
		Column (1) shows subgroups for categorical variables.
		Column (2) indicates the count of missing variables, if any.
		Columns (3)--(5) show means and standard deviations for continuous variables and count and percentage of data for categorical variables, for the full sample, non-consumers of pornography, and consumers of pornography.
		Standard deviations and percentages are in parentheses.
		Column (6) and column (7) report the p-values and standardized mean differences for non-consumers vs consumers.
	}
\end{table}
\fi
